Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-19 paper/paper.tex
decide on tau_c for coherence time Tested everything on bennet.

\fixme{add explanation of correlation function somewhere in the
  following paragraph.  The math could go in theory/methods section.}
{
  \color{red}
  \begin{equation}
    C(\tau) \propto \int
      (N_{\textit{top}}(t) - \bar N_{\textit{top}})
      (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
  \end{equation}
  where...
  \begin{equation}
    C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_0}}
  \end{equation}
  where $T$ is the period and $\tau_0$ is the coherence time.
}

Figure~\ref{corr-pill} shows a plot of the time correlation between
the total MinD found in the two opposite polar regions.  This
normalized value is given by
\begin{equation}
  C(\tau) = \frac{\int
    (N_{\textit{top}}(t) - \bar N_{\textit{top}})
    (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
  }{
    \int
    (N_{\textit{top}}(t) - \bar N_{\textit{top}})
    (N_{\textit{bottom}}(t) - \bar N_{\textit{bottom}})dt
  }
\end{equation}
where $N_{\textit{top}}(t)$ and $N_{\textit{bottom}}(t)$ are the total
MinD proteins in the outer sections of a cell that has been divided
into thirds along its long axis.  These plots heolp us in studying the
periods and the regularity and stability of oscillations.  We have
fitted them to a simple exponential decay model (akin to that of
monochromatic light), given by the equation
\begin{equation}
  C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_0}}
\end{equation}
where $T$ is the period and $\tau_0$ is the coherence time.  In the
case of the stochastic model the pill exhibits coherence times of over
7 periods and in the case of the determinisitic model oscillate
indefinately with complete coherence.

>>>>

Figure~\ref{corr-pill} shows a plot of the time correlation between
the total MinD found in the two opposite polar regions.  This
normalized value is given by
\begin{equation}
  C(\tau) \propto \int
  (N_{\textit{top}}(t) - \bar N_{\textit{top}})
  (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
\end{equation}
where $N_{\textit{top}}(t)$ and $N_{\textit{bottom}}(t)$ are the total
MinD proteins in the outer sections of a cell that has been divided
into thirds along its long axis.  These plots heolp us in studying the
periods and the regularity and stability of oscillations.  We have
fitted them to a simple exponential decay model (akin to that of
monochromatic light), given by the equation
\begin{equation}
  C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_c}}
\end{equation}
where $T$ is the period and $\tau_c$ is the coherence time.  In the
case of the stochastic model the pill exhibits coherence times of over
7 periods and in the case of the determinisitic model oscillate
indefinately with complete coherence.
